---
title: "Simulation Report"
author: ""
date: '`r Sys.Date()`'
output:
  html_document:
    css: "style.css"
    code_folding: show
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
editor_options:
  chunk_output_type: console
---

```{r library, message = FALSE, results = 'hide', echo = FALSE}
# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
library(tidyverse)
library(knitr)
library(ggpubr); 
library(ggrepel)

root <- rprojroot::find_rstudio_root_file()
report_path <- file.path(root)

res_irt <- readRDS(file.path(report_path, "test/test_scaling/twopl_result.rds"))
res_cfa <- readRDS(file.path(report_path, "test/test_scaling/cfa_result.rds"))
```


## Latent variable models

- IRT: $P(y_{ij} = 1 | \eta_i) = \frac{exp(a_j(\eta_i - b_j))}{1 + exp(a_j(\eta_i - b_j))}$

- SEM:  $P(y_{ij} = 1 | \eta_i) = \frac{exp(intercept_j + a_j*\eta_i))}{1 + exp(intercept_j + a_j*\eta_i))}$

- CFA: $y_{ij} = \lambda_j\eta_i + \epsilon_{ij}$

## Condition

- Number of Item: 10
- 

## CFA

### data: first 5 rows

```{r}
head(res_cfa$sim_dt_cfa$original_data)
```


### stan code

For scaling, `transformed parameters` is used to generate new factor loading vector, whose first item is fixed to 1. 

```
transformed parameters {
   vector[nsec] lambda1;
   real linPred[nsecWorked];

   for(j in 1:nsecWorked) {
     if(section[j] == 1)
       lambda1[section[j]] = 1;
     else
       lambda1[section[j]] = lambda[section[j]];
```


```{r}
stan_model <- paste(read_lines(file.path(report_path, "test/test_scaling/stan/CFA.stan")), collapse = "\n")
cat(stan_model)
```



### results

#### Factor loading population vs. estimates
```{r}
fit <- res_cfa$cfa.fit

est <- colMeans(fit[str_detect(names(fit), "lambda1")])
est0 <- colMeans(fit[str_detect(names(fit), "lambda")])[1:10]
cbind(pop = res_cfa$sim_dt_cfa$lv.par, 
      est = est, 
      est_noncont = est0) %>% 
  data.frame(row.names = 1:10) %>% 
  set_names(c("pop_lambda", "est_lambda", "est_nonconst")) %>% 
  mutate_all(round, 3)
```

#### Factor score population vs. estimates

```{r}
eta <- cbind(est_eta = colMeans(fit[str_detect(names(fit), "eta")]), pop_eta = res_cfa$sim_dt_cfa$true_eta)

# Mean of ability
round(colMeans(eta ), 3) 
# SD of ability
round(apply(eta, 2, sd), 3)

plot(eta[,"est_eta"],eta[,"pop_eta"])
```


## IRT

### data: first 5 rows

```{r}
head(res_irt$sim_dt_2pl$original_data)
```


### stan code {.tabset}

Same as before, `transformed parameters` is used for scaling the discrimination and the difficulty parameters. In this case, the first discrimination is fixed to 1, and the first difficulty is fixed to zero (following conventional SEM specification).

```
transformed parameters {
vector[nsec] disc1;
vector[nsec] diff1;

real linPred[nsecWorked];

 for(j in 1:nsecWorked) {
   if(section[j] == 1){
     disc1[section[j]] = 1;
     diff1[section[j]] = 0;
   } else{
     disc1[section[j]] = disc[section[j]];
     diff1[section[j]] = diff[section[j]];
   }
   
   // This specification does work
   linPred[j] = diff1[section[j]] + disc1[section[j]] * eta[studentM[j]];
   
   // This specification does not work
   // linPred[j] = disc1[section[j]] * (eta[studentM[j]] - diff1[section[j]]);
   
 }
}

// To get the difficulty values
generated quantities {
 
 real difficulty[nsec];
 
 for(jj in 1:nsec) {
   difficulty[jj] = - diff1[jj] / disc1[jj];
 }
```

#### This works

```{r}
stan_model <- paste(read_lines(file.path(report_path,"test/test_scaling/stan/IRT_4.stan")), collapse = "\n")
cat(stan_model)
```

#### This din't work

```{r}
stan_model <- paste(read_lines(file.path(report_path,"test/test_scaling/stan/IRT.stan")), collapse = "\n")
cat(stan_model)
```

### results

#### Factor loading population vs. estimates

```{r}
fit <- res_irt$twopl.fit
est_disc <- colMeans(fit[str_detect(names(fit), pattern = "disc1")])
est_diff0 <- colMeans(fit[str_detect(names(fit), "diff1")])
est_diff1 <- colMeans(fit[str_detect(names(fit), "difficulty")])

cbind(pop_disc = res_irt$sim_dt_2pl$lv.par[,1],
      est_disc = est_disc,
      pop_diff = res_irt$sim_dt_2pl$lv.par[,2],
      est_diff = est_diff1,
      est_int = est_diff0) %>% 
  data.frame(row.names = 1:10) %>% 
  set_names(c("pop_disc", "est_disc", "pop_diff", "est_diff", "est_intercept")) %>% mutate_all(round, 3)
```

#### Factor score population vs. estimates

```{r}
eta <- cbind(est_eta = colMeans(fit[str_detect(names(fit), "eta")]), pop_eta = res_irt$sim_dt_2pl$true_eta)

# Mean of ability
round(colMeans(eta ), 3) 
# SD of ability
round(apply(eta, 2, sd), 3)

plot(eta[,"est_eta"],eta[,"pop_eta"])
```







