---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)
library(FLPS)
```

## Fully Latent Principal Stratification (FLPS)

Fully Latent Principal Stratification (**FLPS**) is an extension of principal stratification.

## Install

Install the latest release from CRAN:

```{r}
devtools::install_github("sooyongl/FLPS")
```

The documentation is available at (...)

## Basic working example

### Running with the package

- Set up simulation factors

For latent variable models, Rasch, 2PL, GPCM, and sem (one-factor CFA) are available.

```{r eval = T}
parsFromMod <- list(
  N = 500,              # sample size
  R2Y = 0.2,            # r^2 of outcome
  R2eta = 0.2,          # r^2 of eta by two covariates
  omega = 0.2,          # the effect of eta
  tau0 = 0.13,          # direct effect
  tau1 = -0.06,         # interaction effect between Z and eta
  lambda = 10,          # the mean of administered items
  nsec = 20,            # the number of items
  lvmodel = "Rasch"     # tag for latent variable model; case-nonsensitive
)
```


- Generate a set of simulated data for [`rstan`](https://github.com/stan-dev/rstan) package.

```{r eval = T}
dt <- do.call(FLPS::makeInpData, parsFromMod)
```

`dt` contains three variables: `lv.par`, `true_eta`, and `inp_data`. 

- `lv.par`: information about latent variable models

- `true_eta`: True factor scores

- `inp_data`: a matrix containing all the data for FLPS. It is used in `runFLPS` function.

```{r eval = T}
# Input data matrix
head(dt$inp_data,5)
```

- Fit your FLPS model

Now, provide information about your model. `runFLPS` coverts `inp_data` into the data format for `rstan` given the information, and runs FLPS.

```{r}
res <- FLPS::runFLPS(
  inp_data = sim_dt$inp_data,
  outcome = "Y",
  group = "Z",
  covariate = c("x1","x2"),
  lv_type = "rasch",
  lv_model = paste0("F =~ ", paste(paste0("X", 1:20), collapse = "+")),
  stan_options = list(iter = 4000, warmup = 1000, cores = 1, chains = 4)
)

```
