---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)
library(FLPS)
```

## Fully Latent Principal Stratification (FLPS)

Fully Latent Principal Stratification (**FLPS**) is an extension of principal stratification.

## Install

Install the latest release from CRAN:

```{r}
devtools::install_github("sooyongl/FLPS")
```

The documentation is available at (...)

## Basic working example

### Running with the package

- Generate a simulated rectangular data.
- This data will be converted to a list of data for [`rstan`](https://github.com/stan-dev/rstan) package.
- For latent variable models, Rasch, 2PL, GPCM, and sem (one-factor CFA) are available.


```{r eval = T}
sim_dt <- FLPS::makeInpData(
  N       = 500,  # sample size
  R2Y     = 0.2,  # r^2 of outcome
  R2eta   = 0.5,  # r^2 of eta by two covariates
  omega   = 0.2,  # the effect of eta
  tau0    = 0.13, # direct effect
  tau1    = -0.06,# interaction effect between Z and eta
  linear  = T,    # linearity between the outcome and the covariates
  ydist   = 'n',  # outcome distribution
  lambda  = 0.6,  # the proportion of administered items
  nsec    = 20,   # the total number of items
  nfac    = 1,    # the number of latent factors
  lvmodel = 'rasch' # tag for latent variable model; case-sensitive (use lower-case letters)
)

```

`sim_dt` contains three variables: `sim_info` and `inp_data`. 

- `sim_info`: information about FLPS models

- `inp_data`: a data frame containing all the data for FLPS. It is used in `runFLPS` function.

```{r eval = T}
# Input data matrix
head(sim_dt$inp_data,5)
```

- Fit your FLPS model

Now, provide information about your model. `runFLPS` coverts `inp_data` into the data format for `rstan` given the information, and runs FLPS.

```{r}
res <- FLPS::runFLPS(
  inp_data = sim_dt$inp_data,
  outcome = "Y",
  group = "Z",
  covariate = c("x1","x2"),
  lv_type = "rasch",
  lv_model = paste0("F =~ ", paste(paste0("X", 1:20), collapse = "+")),
  stan_options = list(iter = 4000, warmup = 1000, cores = 1, chains = 4)
)

```
